An Elastica-driven Digital Curve Evolution Model for Image Segmentation\thanks{This work has been partially funded by CoMeDiC ANR-15-CE40-0006 research grant.}

### 2019-11-29 jmiv.tex
Edition of figure 6
Algorithm 2 notation clarification
precision on dataset images resolution

 \Input{A digital set $S$; The ring number $m$; Length($\alpha$), curvature($\beta$) and similarity($\gamma$) coefficients; the maximum number of iterations \MIt;}
 \BlankLine
 $S^{(0)} \longleftarrow S$\;
 $i \longleftarrow 1$\;
 \While{ \It $<$ \MIt  }{ 	
	\comment{Expansion mode}
	\If{ \It is odd }{	 
	 	$X^{(i)} \longleftarrow \argmin_X E_m(X,\overline{S^{(i-1)}})$\;
 		$S^{(i)} \longleftarrow F^{(i-1)} + \overline{X^{(i)}}$\;
 		$S^{(i)} \longleftarrow \overline{S^{(i)}}$\;	 	
 	}
	\comment{Shrinking mode} 	
 	\Else{	
	 	$X^{(i)} \longleftarrow \argmin_X E_m(X,S^{(i-1)})$\; 	
 		$S^{(i)} \longleftarrow F^{(i-1)} + \overline{X^{(i)}}$\;
 	}

@@

\begin{figure}[!h]
\center
\center
\begin{minipage}[b]{0.33\textwidth}
	\subfloat[$r=5, m=1$\label{}]{%
	\includegraphics[scale=0.2]{images/flow/farther-rings/square-r5-l1/summary_flow.eps}
	}%
\end{minipage}%
\begin{minipage}[b]{0.33\textwidth}
	\subfloat[$r=5, m=2$\label{}]{%
	\includegraphics[scale=0.2]{images/flow/farther-rings/square-r5-l2/summary_flow.eps}
	}%
\end{minipage}%
\begin{minipage}[b]{0.33\textwidth}
	\subfloat[$r=5, m=3$\label{}]{%
	\includegraphics[scale=0.2]{images/flow/farther-rings/square-r5-l3/summary_flow.eps}
	}%
\end{minipage}%
\caption{By positioning the estimation ball on farther rings, we minimize artifacts creation. \label{fig:mx-square-flow}}
\end{figure}

@@

We evaluate our method using the BSD300 database \cite{martinFTM01berkeley}. All images contain the same number of pixels, the resolution being 321x481 in portrait mode. We compare the results of our method with segmentations given by GrabCut and Schoenemanns's method \cite{schoenemann09linear}. We report an average of $3s$ per flow iteration, and an average of $30$ iterations per image. While GrabCut executes in less than one second, Schoenemann's method may take several hours to complete.

>>>>

 \Input{A digital set $S$; The ring number $m$; Length($\alpha$), curvature($\beta$) and similarity($\gamma$) coefficients; the maximum number of iterations \MIt;}
 \BlankLine
 $S^{(0)} \longleftarrow S$\;
 $i \longleftarrow 1$\;
 \While{ \It $<$ \MIt  }{ 	
	\comment{Expansion mode}
	\If{ \It is odd }{	 
	 	$X^{(i)} \longleftarrow \argmin_X E_m(X,\overline{S^{(i-1)}})$\;
 		$S^{(i)} \longleftarrow F^{(i-1)}_{\overline{S}} + \overline{X^{(i)}}$\;
 		$S^{(i)} \longleftarrow \overline{S^{(i)}}$\;	 	
 	}
	\comment{Shrinking mode} 	
 	\Else{	
	 	$X^{(i)} \longleftarrow \argmin_X E_m(X,S^{(i-1)})$\; 	
 		$S^{(i)} \longleftarrow F^{(i-1)}_{S} + \overline{X^{(i)}}$\;
 	}

@@

\begin{figure}[!h]
\center
\center
\begin{minipage}[b]{0.33\textwidth}
	\subfloat[$r=5, m=1$\label{}]{%
	\includegraphics[scale=0.2]{images/flow/farther-rings/square-r5-l1/summary_flow.eps}
	}%
\end{minipage}%
\begin{minipage}[b]{0.33\textwidth}
	\subfloat[$r=5, m=3$\label{}]{%
	\includegraphics[scale=0.2]{images/flow/farther-rings/square-r5-l3/summary_flow.eps}
	}%
\end{minipage}%
\begin{minipage}[b]{0.33\textwidth}
	\subfloat[$r=5, m=5$\label{}]{%
	\includegraphics[scale=0.2]{images/flow/farther-rings/square-r5-l5/summary_flow.eps}
	}%
\end{minipage}%
\caption{By positioning the estimation ball on farther rings, we minimize artifacts creation. \label{fig:mx-square-flow}}
\end{figure}

@@

We evaluate our method using the BSD300 database \cite{martinFTM01berkeley}. All images contain the same number of pixels, the resolution being 321x481 (481x321) in portrait (landscape) mode. We compare the results of our method with segmentations given by GrabCut and Schoenemanns's method \cite{schoenemann09linear}. We report an average of $3s$ per flow iteration, and an average of $30$ iterations per image. While GrabCut executes in less than one second, Schoenemann's method may take several hours to complete.
